{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-10-08 thesis/related.tex
parallel dpor in related

To date a number of techniques have been proposed to mitigate exponential explosion,
the Sisyphean rock of SCT.
The notion that some interleavings of concurrent threads could lead to indistinguishable program states and be therefore redundant,
known as {\em partial order reduction} (POR),
was first proposed in \cite{partial-model-checking}
and explored in detail in \cite{partial-order-methods}.
{\em Dynamic POR} (DPOR) was later developed in \cite{dpor},
proposing to track communication events between threads on-the-fly (i.e., dynamically)
rather than to rely on imprecise static alias analyses,
and is now considered the baseline for all subsequent state space reduction approaches in SCT.
That paper includes the {\em sleep sets} extension,
which Landslide includes in its implementation.
It is a {\em sound} reduction algorithm, meaning it will never fail to test a possible program behavior, despite skipping many execution sequences.
\sect{\ref{sec:landslide-dpor}} provides a detailed walk-through of how DPOR works,
as many of this thesis's contributions build directly upon it.
%
DPOR has since been extended in several ways to achieve further reduction
and to incorporate new concurrency models.
Optimal DPOR \cite{optimal-dpor} extends sleep sets into the more expressive {\em wakeup trees},
which provably tests exactly one interleaving from each equivalence class,
i.e., the optimal possible reduction,
at least under the memory independence definition of equivalence.
Extending the equivalence relation itself to capture not just memory {\em address} conflicts
but also the {\em values} read and written,
SATCheck \cite{satcheck} and Maximal Causality Reduction (MCR) \cite{mcr}
use an SMT solver \cite{z3} to identify additional pruning opportunities.
Implementing wakeup trees or SMT-driven exploration in Landslide is left to future work.

>>>>

To date a number of techniques have been proposed to mitigate exponential explosion,
the Sisyphean rock of SCT.
The notion that some interleavings of concurrent threads could lead to indistinguishable program states and be therefore redundant,
known as {\em partial order reduction} (POR),
was first proposed in \cite{partial-model-checking}
and explored in detail in \cite{partial-order-methods}.
{\em Dynamic POR} (DPOR) was later developed in \cite{dpor},
proposing to track communication events between threads on-the-fly (i.e., dynamically)
rather than to rely on imprecise static alias analyses,
and is now considered the baseline for all subsequent state space reduction approaches in SCT.
That paper includes the {\em sleep sets} extension,
which Landslide includes in its implementation.
It is a {\em sound} reduction algorithm, meaning it will never fail to test a possible program behavior, despite skipping many execution sequences.
\sect{\ref{sec:landslide-dpor}} provides a detailed walk-through of how DPOR works,
as many of this thesis's contributions build directly upon it.
%
DPOR has since been extended in several ways to achieve further reduction
and to incorporate new concurrency models.
\revision{Distributed DPOR \cite{parallel-dpor}
allows the exploration to be parallelized,
with a minimum of overhead from redundant interleavings that would ordinarily be pruned in sequential DPOR.}
Optimal DPOR \cite{optimal-dpor} extends sleep sets into the more expressive {\em wakeup trees},
which provably tests exactly one interleaving from each equivalence class,
i.e., the optimal possible reduction,
at least under the memory independence definition of equivalence.
Extending the equivalence relation itself to capture not just memory {\em address} conflicts
but also the {\em values} read and written,
SATCheck \cite{satcheck} and Maximal Causality Reduction (MCR) \cite{mcr}
use an SMT solver \cite{z3} to identify additional pruning opportunities.
Implementing parallelization, wakeup trees, or SMT-driven exploration in Landslide is left to future work.
